\begin{rubric}{Work Experience}
\entry*[2026 Mar -- Now]%
	\textbf{Applied Scientist II} in Amazon;
  
   \textbf{\textit{Medical Foundation Model;}} Built and trained a medical foundation model from scratch with multiple modules integrating heterogeneous data sources, including EHR records, claims data, drug SMILES, and patient genomic data.)
   
\entry*[2026 Mar -- Now]%
	\textbf{Affiliated Lecturer} in Yale School of Medicine;



\entry*[2024 Jun -- 2026 Feb]%
	\textbf{Post-doctoral Researcher} in  Yale University, School of Medicine, \emph{Advisor: Dr. Lucila Ohno-Machado}; 
  
   \textbf{\textit{DNA Large Language Model;}}   Designed downstream applications based on a DNA large language model (Evo2): performed continued pretraining on human pan-genome data to “humanize” the model for human genetic variation, and supervised fine-tuning on disease-labeled human genomics datasets for clinical prediction tasks.
 
  \textbf{\textit{LLM Model Compression;}} Implemented model compression for the DNA LLM (Evo2) to enable more efficient inference on much longer genomic sequences.
  
 \textbf{\textit{Tabular Large Foundation Model;}} Built applications on top of the tabular foundation model TabPFN by fine-tuning it on clinical datasets, achieving performance that outperforms standard gradient-boosting–based methods.


\entry*[2023 May-August]%
	\textbf{Software Engineer} in The Trade Desk
    
\textbf{\textit{Adversarial Model;}} Developed a deep learning–based adversarial model to predict competitors (such as Google Ads) bidding for on-page impressions.


% Blank lines result in extra space!
\entry*[2018 May-August]%
	\textbf{Data Scientist} Union Pay Lab 
	
    \textbf{\textit{Community detection;}} 
To build this community detection model.
One patent was applied in this project(Patent number: CN09493086A, Patent page: http://www.soopat.com/Patent/201811261870). 

\entry*[2016 -- 2017]%
	\textbf{Data Scientist} in Lenovo; 
	
 \textbf{\textit{Text Classification;}} Text classification model for online sentiment analysis of customer comments in e-commerce. 
 
  \textbf{\textit{Fake Comments Detection in E-commerce;}} Identify whether a comment from e-commerce is from a real user or a machine.
  
 \textbf{\textit{Retailer Fraud Detection;}} To detect Insurance and warranty frauds in Retailers of Lenovo.


    
	
%  \textbf{\textit{Text Classification;}} Model defense and attack.
%    \textbf{\textit{Money laundry detection;}} I used Union Pay money laundry dataset, leveraged Graph convolutional neural network(GCN), and Random Forest technologies to detect and predict money laundry behavior. Our new model can reach a 96\% accuracy rate in the Union pay dataset, which outperformed the previous prediction model by 3\%. Particularly, when the Money laundry network size is large, this model can out-performance 7\% compared with the previous model.  

%


% \entry*[2024 -- now]%
  % \begin{tabular}{@{}l}
  %   \textbf{Post-doctoral Fellow, Yale University}, School of Medicine \\
  %   \emph{Advisor: Dr. Lucila Ohno-Machado}
  % \end{tabular}



    
\end{rubric}